---
title: "Intro to Data Programming"
---



<br><br/>
  
This is an introductory class to data programming using the R language.

<br><br/>




### [Lecture 01](Lecture_01-00-Introduction_to_R.html): Getting Started

Some text describing the contents of the chapter.  



### [Lecture 02](Lecture_02-00_Data_Structures.html): Data Structures

Some text describing the contents of the chapter.  



### [Lecture 03](Lecture_01-00-Introduction_to_R.html): Importing Data

Some text describing the contents of the chapter.  



### [Lecture 04](Lecture_02-00_Data_Structures.html): Combining Datasets

Some text describing the contents of the chapter.  





<br><br/>
<br><br/>
  
  
  
  
  


```{r, echo=F, message=F, fig.width=4, fig.align='center'}

# devtools::install_github("garthtarr/pairsD3")

data(iris)
require(pairsD3)
pairsD3(iris[,1:4],group=iris[,5])
```



  
  
  
  
  


```{r, echo=F, fig.width=4, fig.align='center'}

library( networkD3 )

URL <- paste0(
        "https://cdn.rawgit.com/christophergandrud/networkD3/",
        "master/JSONdata/energy.json")
Energy <- jsonlite::fromJSON(URL)
# Plot
sankeyNetwork(Links = Energy$links, Nodes = Energy$nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             units = "TWh", fontSize = 12, nodeWidth = 30)
```





  
  
  
  
  
  
  


```{r, echo=F, fig.width=4, fig.align='center'}

# devtools::install_github("timelyportfolio/sunburstR")

library(sunburstR)

# read in sample visit-sequences.csv data provided in source
#   https://gist.github.com/kerryrodden/7090426#file-visit-sequences-csv
sequence_data <- read.csv(
  paste0(
    "https://gist.githubusercontent.com/kerryrodden/7090426/"
    ,"raw/ad00fcf422541f19b70af5a8a4c5e1460254e6be/visit-sequences.csv"
  )
  ,header=F
  ,stringsAsFactors = FALSE
)

sunburst(sequence_data)


```



  
  
  
  
  
